Nabi - A Preventative Solution Against JavaScript and Scriptless Tabnabbing Attacks

### 2015-05-06 paper/paper.tex
Fleshed out conclusion

We have devloped a system to block tabnabbing attacks that still allows the user to retain most of the JavaScript functionality they need to securely browse the Internet while without just only detecting and alerting the user.

>>>>

We have proposed a solution for preventing tabnabbing attacks and begun development of a browser extension to implement the different aspects of this solution. Tabnabbing attacks are already inherently clever in their design, so it is very difficult to develop a detection metric capable of identifying tabnabbing attacks without using computationally expensive algorithms or generating an extensive amount of false positives. Our preventative approach provides a solution that stops tabnabbing without resorting to either of these shortcomings. Once it meets all of our proposed system aspects, the Nabi extension will be capable of preventing both script-based and scriptless tabnabbing attacks without unnecessarily burdening the user with a weighty detection-based browser add-on or constantly warning the user about harmless false positives. More so, a detection-based solution that cannot successfully identify all tabnabbing attacks leaves the user with a false sense of security, leaving them vulnerable if they are overly confident in the faulty detection algorithm. This further justifies the use of a preventative method as it can provably prevent all script-based versions of the tabnabbing attack.
